|

### 2019-06-27 inst/manuscript/manuscript.Rmd
Fix yeast sample labels in manuscript
Change figure 1 to figure S1
Also:
 - Update title, running title, authors, affiliations, corresponding
   author

---
title: | 
   **Defining protein markers for *Candida albicans* extracellular vesicles**
author: | 
   *Charlotte Dawson^a^, Mark Bleackley^a^, Donovan Garcia Ceron^a^, 
   Marilyn Anderson^a^*
date: | 
   *^a^Department of Biochemistry and Genetics, La Trobe Institute for 
   Molecular Science, La Trobe University, Victoria, 3086, Australia*
output: 
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
bibliography: "components/references.bib" 
csl: "components/molecular-and-cellular-proteomics.csl"
link-citations: yes
linkcolor: black
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \usepackage{lipsum}
  - \pagestyle{fancy}
  - \fancyhead[L]{This is the running title it is rather long}
  - \setlength{\headheight}{15pt}
  - \usepackage{float}
  - \let\origfigure\figure
  - \let\endorigfigure\endfigure
  - \renewenvironment{figure}[1][2]{\expandafter\origfigure\expandafter[H]}
    {\endorigfigure}
  - \usepackage{caption}
  - \captionsetup{font={normalsize,stretch=1.3},labelfont=bf}
  - \usepackage{threeparttable}
---

**Running title:** Running title goes here

**Corresponding author:**

@@

# drop EV_1 and WCL_1 samples
yeast_lfq2 <- yeast_lfq[, !colnames(yeast_lfq) %in% c("EV_1", "WCL_1")]

@@

```{r table1}
tab1_cap <- "\\textbf{Candidate positive protein markers for 
             \\textit{C. albicans} EVs.} This list of proteins consists of 
             those that were found to be exclusive to EVs or significantly 
             enriched in EVs across the four \\textit{C. albicans} strains 
             examined in this study. Proteins are grouped according to their 
             subcellular localisation as annotated in the Candida Genome 
             Database (candidagenome.org) (ref:footnote1). 
             The log\\textsubscript{2} ratio of the abundance (mean MaxQuant 
             LFQ intensity) of each protein in EVs compared to whole cell 
             lysate (WCL) for each strain is listed. \`\`ex\" indicates where 
             a protein was only quantified in the EV fraction and not the WCL 
             for that strain. The \`\`TM\" column indicates the number of 
             transmembrane domains for each protein as annotated in UniProtKB. 
             \`\`SP\" indicates whether a protein is annotated as having a 
             signal peptide according to UniProtKB. \`\`VDM\" shows whether a 
             protein has previously been detected in vesicle-depleted culture 
             media (i.e. the proteins may also be in the soluble secretome) 
             (ref:table1). Underlined proteins are those identified as the 
             best candidates for positive EV markers according to the 
             criteria depicted in Figure \\ref{fig:figure1}."

@@

```{r figure1, fig.cap=f1_cap, fig.width=5.45, fig.height=6}
# construct figure 1
f1_cap <- "\\textbf{Schematic of the workflow used for the isolation and 
           proteomic analysis of \\textit{C. albicans} EVs and the selection 
           of EV protein markers.} Steps 1 to 6 were performed for each of the 
           four strains examined in this study: DAY286 yeast, ATCC90028 yeast, 
           ATCC10231 yeast, and DAY286 biofilm. The results from the four 
           seperate analyses were combined (step 7) to identify proteins which 
           commonly appeared as EV marker candidates. The MISEV2018 criteria 
           for protein content-based EV characterisation and other 
           considerations were used to select the best \\textit{C. albicans} 
           EV marker proteins."

f1 <- png::readPNG("figures/figure1.png")

# draw figure 1
ggplot() + 
  background_image(f1)
```

```{r figure2Data, include=FALSE}
# construct data.frame with nta experiment info
nta_metadata <- data.frame(id = c("ATCC10231_1", "ATCC10231_2", "ATCC10231_3", 
                                  "ATCC90028_1", "ATCC90028_2", "ATCC90028_3", 
                                  "Biofilm_1", "Biofilm_2", "Biofilm_3", 
                                  "Biofilm_4", "Biofilm_5", 
                                  "DAY286_1", "DAY286_2", "DAY286_3"), 
                           protein_conc = c(0.192, 0.282, 0.287, 
                                            0.424, 0.716, 0.584, 
                                            0.204, 0.198, 0.297, 0.193, 0.416, 
                                            0.437, 0.360, 0.447), 
                           stringsAsFactors = FALSE)

@@

```{r figure2plots, include=FALSE}
# construct figure 2a
f2a_img <- png::readPNG("figures/figure2a.png")

f2a <- ggplot() + 
  background_image(f2a_img) + 
  theme(plot.margin = margin(t = 0.3, l = 0, r = 0, b = 0, unit = "inches"))

# construct figure 2b
f2b <- nta_bioavg %>% 
  ggplot(aes(x = particle_size, y = Bio_rep_mean, colour = Strain)) + 
  scale_colour_manual(values = st_pal[c(3, 2, 4, 1)], 
                      breaks = c("DAY286", "ATCC90028", 
                                 "ATCC10231", "Biofilm"), 
                      labels = c("DAY286 Y", "ATCC90028", 
                                 "ATCC10231", "DAY286 B")) + 
  geom_vline(xintercept = 100, colour = "#999999", linetype = "dashed") +
  geom_line(size = 0.5) + 
  facet_wrap(~ facet, scales = "free", ncol = 2, nrow = 1) + 
  theme_classic() + 
  theme(strip.background = element_blank(), 
        strip.text = element_blank(), 
        legend.position = c(0.88, 0.6), 
        legend.title = element_blank(), 
        plot.margin = margin(t = 0.2, l = 0, r = 0.2, b = 0, unit = "inches"), 
        axis.text.x = element_text(colour = "black")) + 
  xlab(label = "Particle size (nm)") + 
  ylab(label = "Particles / mL")

@@

f2c <- nta_total %>% 
  ggboxplot(x = "Strain", y = "part_per_prot", 
            color = "Strain", palette = st_pal, add = "jitter", 
            add.params = list(color = "black"), 
            shape = 15,
            ylab = expression("Particles /"~paste(mu,g)~"protein"))
f2c <- ggpar(f2c, 
             yscale = "log10", 
             format.scale = TRUE, 
             ylim = c(8e8, 8e10),
             font.y = 10, 
             legend = "none") + 
  stat_pvalue_manual(nta_total_tukey[c(2,4,6), ], label = "p.adj", 
                     y.position = c(10.45, 10.65, 10.85), 
                     tip.length = 1e-2, 
                     label.size = 3) + 
  theme(axis.title.x = element_blank(), 
        plot.margin = margin(t = 0.2, l = 0.2, r = 0, b = 0.15, 
                             unit = "inches")) + 
  scale_x_discrete(labels = c("ATCC90028" = "A9", 
                              "ATCC10231" = "A1", 
                              "Biofilm" = "B", 
                              "DAY286" = "Y"))
```

```{r figure2, fig.cap=f2_cap, fig.width=7.1, fig.height=4}
# draw figure 2
ggarrange(f2a, 
          ggarrange(f2b, f2c, 
                    labels = c("B", "C"), 
                    ncol = 2,
                    nrow = 1, 
                    widths = c(1.8,1)), 
          labels = c("A", ""), 
          nrow = 2, 
          ncol = 1, 
          heights = c(1,1))

f2_cap <- "\\textbf{Characterisation and quantification of EVs from different 
           \\textit{C. albicans} strains.} \\textit{(A)} Representative TEM 
           images of EVs isolated from 4 different \\textit{C. albicans} 
           strains. Scale bar indicates 0.5 $\\mu$m. \\textit{(B)} Size 
           distribution of DAY286 yeast (n = 3), ATCC90028 yeast (n = 3), 
           ATCC10231 yeast (n = 3), and DAY286 biofilm (n = 5) EVs as measured 
           by nanoparticle tracking analysis. Line plots shown are the average 
           of the biological replicates and the dashed grey line indicates 100 
           nm. Plots for the individual biological replicates are presented in 
           supplemental Figure S1. \\textit{(C)} Comparison of the ratio of 
           particle concentration to protein concentration of the EV fraction, 
           (particles/mL) $\\div$ ($\\mu$g protein/mL), across the four EV 
           sources. Each dot represents one biological replicate. Sample means 
           were compared using ANOVA followed by Tukey's HSD \\textit{post-hoc} 
           test. P-values indicating significant differences are shown. The 
           particle and protein concentrations for each biological replicate 
           are provided in supplemental Table S1."
```

@@

```{r figure3Yeast, include=FALSE}
# compare DAY286 yeast EV WCL proteins
f3a1 <- plot_venn(list("EV" = y_ev, "WCL" = y_wcl), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans", 
                  cex = 0.8,
                  cat.fontfamily = "sans", 
                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
                  margin = 0.05)

# DAY286 yeast venn
f3a1 <- as_ggplot(f3a1) + 
  theme(plot.margin = unit(c(1,0.5,1,0.5), "lines")) + 
  annotate("text", x = 0.5, y = 0.92, 
           label = "bold('DAY286 yeast')", parse = TRUE)

# generate volcano plot
f3b1 <- plot_volcano(data = yeast_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched", 
                                 "WCL enriched", 
                                 "Not significant"), 
                      values = unname(ev_pal[c(2,1,3)]), 
                      breaks = c("EV up", "WCL up", "not sig"), 
                      name = element_blank()) + 
  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 Y')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('88')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('88')", parse = TRUE, 
           colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('318')", parse = TRUE, 
           colour = unname(ev_pal[1]))
```

```{r figure3A9, include=FALSE}
# compare ATCC90028 EV WCL proteins
f3a2 <- plot_venn(list("EV" = atcc9_ev, "WCL" = atcc9_w), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans",
                  cex = 0.8,
                  cat.fontfamily = "sans", 
                  cat.just = list(c(0.5,1.7), c(0.5,1.55)), 
                  ext.percent = c(30,10,0),
                  ext.pos = c(45,315),
                  ext.dist = -0.05,
                  ext.length = 0.5,
                  margin = 0.05)

# ATCC90028 venn
f3a2 <- as_ggplot(f3a2) + 
  theme(plot.margin = unit(c(1,0,1,0.5), "lines")) + 
  annotate("text", x = 0.5, y = 0.92, label = "bold('ATCC90028')", parse = TRUE)

# generate volcano plot
f3b2 <- plot_volcano(data = a9_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched (99)", "WCL enriched (130)", 
                                 "Not significant (744)"),
                      values = unname(ev_pal[c(2,3,1)])) + 
  annotate("text", x = 8, y = 0.5, label = "bold('ATCC90028')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('99')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('130')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('744')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

```{r figure3A1, include=FALSE}
# compare ATCC10231 EV WCL proteins
f3a3 <- plot_venn(list("EV" = atcc1_ev, "WCL" = atcc1_w), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans", 
                  cex = 0.8,
                  cat.fontfamily = "sans",
                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
                  ext.percent = c(0,20,0),
                  ext.pos = 45,
                  ext.dist = -0.05,
                  ext.length = 0.5,
                  margin = 0.05)

# ATCC10231 venn
f3a3 <- as_ggplot(f3a3) + 
  theme(plot.margin = unit(c(1,0.5,1,0.5), "lines")) + 
  annotate("text", x = 0.5, y = 0.92, label = "bold('ATCC10231')", parse = TRUE)

# generate volcano plot
f3b3 <- plot_volcano(data = a1_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched (108)", "WCL enriched (142)", 
                                 "Not significant (435)"),
                      values = unname(ev_pal[c(2,3,1)])) + 
  annotate("text", x = 8, y = 0.5, label = "bold('ATCC10231')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('106')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('134')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('445')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

```{r figure3Biofilm, include=FALSE}
# compare DAY286 biofilm EV WCL proteins
f3a4 <- plot_venn(list("EV" = b_ev, "WCL" = b_wcl), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans", 
                  cex = 0.8, 
                  cat.fontfamily = "sans", 
                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
                  ext.text = TRUE,
                  ext.percent = c(20,10,0),
                  ext.pos = c(45,315),
                  ext.dist = -0.1,
                  ext.length = 0.5,
                  margin = 0.05)
# DAY286 biofilm venn
f3a4 <- as_ggplot(f3a4) + 
  theme(plot.margin = unit(c(1,0,1,0), "lines")) + 
  annotate("text", x = 0.5, y = 0.92, label = "bold('DAY286 biofilm')", 
           parse = TRUE)

# generate volcano plot
f3b4 <- plot_volcano(data = biofilm_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched (95)", "WCL enriched (79)", 
                                 "Not significant (484)"), 
                      values = unname(ev_pal[c(2,1,3)]), 
                      breaks = c("EV up", "WCL up", "not sig")) + 
  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 B')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('95')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('79')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('484')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

```{r figure3, fig.cap=f3_cap, fig.width=7.1, fig.height=6}
# draw figure 3
ggarrange(ggarrange(f3a1, f3a2, f3a3, f3a4, 
                    labels = c("A", "", "", ""), 
                    ncol = 4, 
                    nrow = 1, 
                    align = "v"), 
          ggarrange(f3b1, f3b2,
                    f3b3, f3b4, 
                    labels = c("B", rep("", 3)), 
                    ncol = 2, 
                    nrow = 2, 
                    align = "hv", 
                    common.legend = TRUE, 
                    legend = "right", 
                    widths = c(1,1), 
                    vjust = 1), 
          ncol = 1,
          nrow = 2, 
          heights = c(1,2))

>>>>

---
title: | 
   **Protein markers for *Candida albicans* EVs include claudin-like Sur7 
   family proteins and GTPases**
author: | 
   | Charlotte Dawson^a^, Donovan Garcia Ceron^a^, Harinda Rajapaksha^b^, 
     Pierre Faou^b^,
   | Marilyn Anderson^a^, Mark Bleackley^a^
date: | 
   | *^a^Department of Biochemistry and Genetics, La Trobe Institute for 
     Molecular Science, La Trobe University, 
     Melbourne, 3086, Victoria, Australia*
   | *^b^La Trobe Comprehensive Proteomics Platform, La Trobe Institute for 
     Molecular Science, La Trobe University, Melbourne, 
     3086, Victoria, Australia*
output: 
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
bibliography: "components/references.bib" 
csl: "components/molecular-and-cellular-proteomics.csl"
link-citations: yes
linkcolor: black
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \usepackage{lipsum}
  - \pagestyle{fancy}
  - \fancyhead[L]{Defining \textit{Candida albicans} EV protein markers}
  - \setlength{\headheight}{15pt}
  - \usepackage{float}
  - \let\origfigure\figure
  - \let\endorigfigure\endfigure
  - \renewenvironment{figure}[1][2]{\expandafter\origfigure\expandafter[H]}
    {\endorigfigure}
  - \usepackage{caption}
  - \captionsetup{font={normalsize,stretch=1.3},labelfont=bf}
  - \usepackage{threeparttable}
---

**Corresponding author:** Mark Bleackley, m.bleackley@latrobe.edu.au

**Running title:** Defining _Candida albicans_ EV protein markers

@@

# drop EV_1 and WCL_1 samples
yeast_lfq2 <- yeast_lfq[, !colnames(yeast_lfq) %in% c("EV_0", "WCL_0")]

@@

```{r table1}
tab1_cap <- "\\textbf{Candidate positive protein markers for 
             \\textit{C. albicans} EVs.} This list of proteins consists of 
             those that were found to be exclusive to EVs or significantly 
             enriched in EVs across the four \\textit{C. albicans} strains 
             examined in this study. Proteins are grouped according to their 
             subcellular localisation as annotated in the Candida Genome 
             Database (candidagenome.org) (ref:footnote1). 
             The log\\textsubscript{2} ratio of the abundance (mean MaxQuant 
             LFQ intensity) of each protein in EVs compared to whole cell 
             lysate (WCL) for each strain is listed. \`\`ex\" indicates where 
             a protein was only quantified in the EV fraction and not the WCL 
             for that strain. The \`\`TM\" column indicates the number of 
             transmembrane domains for each protein as annotated in UniProtKB. 
             \`\`SP\" indicates whether a protein is annotated as having a 
             signal peptide according to UniProtKB. \`\`VDM\" shows whether a 
             protein has previously been detected in vesicle-depleted culture 
             media (i.e. the proteins may also be in the soluble secretome) 
             (ref:table1). Underlined proteins are those identified as the 
             best candidates for positive EV markers according to the 
             criteria depicted in supplemental Figure S1."

@@

```{r figure1Data, include=FALSE}
# construct data.frame with nta experiment info
nta_metadata <- data.frame(id = c("ATCC10231_1", "ATCC10231_2", "ATCC10231_3", 
                                  "ATCC90028_1", "ATCC90028_2", "ATCC90028_3", 
                                  "Biofilm_1", "Biofilm_2", "Biofilm_3", 
                                  "Biofilm_4", "Biofilm_5", 
                                  "DAY286_1", "DAY286_2", "DAY286_3"), 
                           protein_conc = c(0.192, 0.282, 0.287, 
                                            0.424, 0.716, 0.584, 
                                            0.204, 0.198, 0.297, 0.193, 0.416, 
                                            0.437, 0.360, 0.447), 
                           stringsAsFactors = FALSE)

@@

```{r figure1plots, include=FALSE}
# construct figure 1a
f1a_img <- png::readPNG("figures/figure1a.png")

f1a <- ggplot() + 
  background_image(f1a_img) + 
  theme(plot.margin = margin(t = 0.3, l = 0, r = 0, b = 0, unit = "inches"))

# construct figure 1b
f1b <- nta_bioavg %>% 
  ggplot(aes(x = particle_size, y = Bio_rep_mean, colour = Strain)) + 
  scale_colour_manual(values = st_pal[c(3, 2, 4, 1)], 
                      breaks = c("DAY286", "ATCC90028", 
                                 "ATCC10231", "Biofilm"), 
                      labels = c("DAY286 Y", "ATCC90028", 
                                 "ATCC10231", "DAY286 B")) + 
  geom_vline(xintercept = 100, colour = "#999999", linetype = "dashed") +
  geom_line(size = 0.5) + 
  facet_wrap(~ facet, scales = "free", ncol = 2, nrow = 1) + 
  theme_classic() + 
  theme(strip.background = element_blank(), 
        strip.text = element_blank(), 
        legend.position = c(0.88, 0.6), 
        legend.title = element_blank(), 
        plot.margin = margin(t = 0.2, l = 0, r = 0.2, b = 0, unit = "inches"), 
        axis.text.x = element_text(colour = "black")) + 
  xlab(label = "Particle size (nm)") + 
  ylab(label = "Particles / mL")

@@

f1c <- nta_total %>% 
  ggboxplot(x = "Strain", y = "part_per_prot", 
            color = "Strain", palette = st_pal, add = "jitter", 
            add.params = list(color = "black"), 
            shape = 15,
            ylab = expression("Particles /"~paste(mu,g)~"protein"))
f1c <- ggpar(f1c, 
             yscale = "log10", 
             format.scale = TRUE, 
             ylim = c(8e8, 8e10),
             font.y = 10, 
             legend = "none") + 
  stat_pvalue_manual(nta_total_tukey[c(2,4,6), ], label = "p.adj", 
                     y.position = c(10.45, 10.65, 10.85), 
                     tip.length = 1e-2, 
                     label.size = 3) + 
  theme(axis.title.x = element_blank(), 
        plot.margin = margin(t = 0.2, l = 0.2, r = 0, b = 0.15, 
                             unit = "inches")) + 
  scale_x_discrete(labels = c("ATCC90028" = "A9", 
                              "ATCC10231" = "A1", 
                              "Biofilm" = "B", 
                              "DAY286" = "Y"))
```

```{r figure1, fig.cap=f1_cap, fig.width=7.1, fig.height=4}
# draw figure 1
ggarrange(f1a, 
          ggarrange(f1b, f1c, 
                    labels = c("B", "C"), 
                    ncol = 2,
                    nrow = 1, 
                    widths = c(1.8,1)), 
          labels = c("A", ""), 
          nrow = 2, 
          ncol = 1, 
          heights = c(1,1))

f1_cap <- "\\textbf{Characterisation and quantification of EVs from different 
           \\textit{C. albicans} strains.} \\textit{(A)} Representative TEM 
           images of EVs isolated from 4 different \\textit{C. albicans} 
           strains. Scale bar indicates 0.5 $\\mu$m. \\textit{(B)} Size 
           distribution of DAY286 yeast (n = 3), ATCC90028 yeast (n = 3), 
           ATCC10231 yeast (n = 3), and DAY286 biofilm (n = 5) EVs as measured 
           by nanoparticle tracking analysis. Line plots shown are the average 
           of the biological replicates and the dashed grey line indicates 100 
           nm. Plots for the individual biological replicates are presented in 
           supplemental Figure S2. \\textit{(C)} Comparison of the ratio of 
           particle concentration to protein concentration of the EV fraction, 
           (particles/mL) $\\div$ ($\\mu$g protein/mL), across the four EV 
           sources. Each dot represents one biological replicate. Sample means 
           were compared using ANOVA followed by Tukey's HSD \\textit{post-hoc} 
           test. P-values indicating significant differences are shown. The 
           particle and protein concentrations for each biological replicate 
           are provided in supplemental Table S1."
```

@@

```{r figure2Yeast, include=FALSE}
# compare DAY286 yeast EV WCL proteins
f2a1 <- plot_venn(list("EV" = y_ev, "WCL" = y_wcl), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans", 
                  cex = 0.8,
                  cat.fontfamily = "sans", 
                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
                  margin = 0.05)

# DAY286 yeast venn
f2a1 <- as_ggplot(f2a1) + 
  theme(plot.margin = unit(c(1,0.5,1,0.5), "lines")) + 
  annotate("text", x = 0.5, y = 0.92, 
           label = "bold('DAY286 yeast')", parse = TRUE)

# generate volcano plot
f2b1 <- plot_volcano(data = yeast_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched", 
                                 "WCL enriched", 
                                 "Not significant"), 
                      values = unname(ev_pal[c(2,1,3)]), 
                      breaks = c("EV up", "WCL up", "not sig"), 
                      name = element_blank()) + 
  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 Y')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('88')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('88')", parse = TRUE, 
           colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('318')", parse = TRUE, 
           colour = unname(ev_pal[1]))
```

```{r figure2A9, include=FALSE}
# compare ATCC90028 EV WCL proteins
f2a2 <- plot_venn(list("EV" = atcc9_ev, "WCL" = atcc9_w), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans",
                  cex = 0.8,
                  cat.fontfamily = "sans", 
                  cat.just = list(c(0.5,1.7), c(0.5,1.55)), 
                  ext.percent = c(30,10,0),
                  ext.pos = c(45,315),
                  ext.dist = -0.05,
                  ext.length = 0.5,
                  margin = 0.05)

# ATCC90028 venn
f2a2 <- as_ggplot(f2a2) + 
  theme(plot.margin = unit(c(1,0,1,0.5), "lines")) + 
  annotate("text", x = 0.5, y = 0.92, label = "bold('ATCC90028')", parse = TRUE)

# generate volcano plot
f2b2 <- plot_volcano(data = a9_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched (99)", "WCL enriched (130)", 
                                 "Not significant (744)"),
                      values = unname(ev_pal[c(2,3,1)])) + 
  annotate("text", x = 8, y = 0.5, label = "bold('ATCC90028')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('99')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('130')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('744')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

```{r figure2A1, include=FALSE}
# compare ATCC10231 EV WCL proteins
f2a3 <- plot_venn(list("EV" = atcc1_ev, "WCL" = atcc1_w), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans", 
                  cex = 0.8,
                  cat.fontfamily = "sans",
                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
                  ext.percent = c(0,20,0),
                  ext.pos = 45,
                  ext.dist = -0.05,
                  ext.length = 0.5,
                  margin = 0.05)

# ATCC10231 venn
f2a3 <- as_ggplot(f2a3) + 
  theme(plot.margin = unit(c(1,0.5,1,0.5), "lines")) + 
  annotate("text", x = 0.5, y = 0.92, label = "bold('ATCC10231')", parse = TRUE)

# generate volcano plot
f2b3 <- plot_volcano(data = a1_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched (108)", "WCL enriched (142)", 
                                 "Not significant (435)"),
                      values = unname(ev_pal[c(2,3,1)])) + 
  annotate("text", x = 8, y = 0.5, label = "bold('ATCC10231')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('106')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('134')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('445')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

```{r figure2Biofilm, include=FALSE}
# compare DAY286 biofilm EV WCL proteins
f2a4 <- plot_venn(list("EV" = b_ev, "WCL" = b_wcl), 
                  use_uniprot = TRUE, type = "plot", 
                  fontfamily = "sans", 
                  cex = 0.8, 
                  cat.fontfamily = "sans", 
                  cat.just = list(c(0.5,1.7), c(0.5,1.5)), 
                  ext.text = TRUE,
                  ext.percent = c(20,10,0),
                  ext.pos = c(45,315),
                  ext.dist = -0.1,
                  ext.length = 0.5,
                  margin = 0.05)
# DAY286 biofilm venn
f2a4 <- as_ggplot(f2a4) + 
  theme(plot.margin = unit(c(1,0,1,0), "lines")) + 
  annotate("text", x = 0.5, y = 0.92, label = "bold('DAY286 biofilm')", 
           parse = TRUE)

# generate volcano plot
f2b4 <- plot_volcano(data = biofilm_res, 
                     p_val = adj.P.Val, 
                     log2fc = logFC,
                     group = group, 
                     label_fun = ifelse(logFC >= 8, CGD_gene_name, ""), 
                     point_size = 0.6, 
                     label_size = 2, 
                     x_lim = c(-10, 12), 
                     y_lim = c(0, 8), 
                     legend_params = c("left", 11, 8), 
                     axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("EV enriched (95)", "WCL enriched (79)", 
                                 "Not significant (484)"), 
                      values = unname(ev_pal[c(2,1,3)]), 
                      breaks = c("EV up", "WCL up", "not sig")) + 
  annotate("text", x = 8.5, y = 0.5, label = "bold('DAY286 B')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('95')", 
           parse = TRUE, colour = unname(ev_pal[2])) + 
  annotate("text", x = -3.5, y = 7, label = "bold('79')", 
           parse = TRUE, colour = unname(ev_pal[3])) + 
  annotate("text", x = 0, y = 6, label = "bold('484')", 
           parse = TRUE, colour = unname(ev_pal[1]))
```

```{r figure2, fig.cap=f2_cap, fig.width=7.1, fig.height=6}
# draw figure 2
ggarrange(ggarrange(f2a1, f2a2, f2a3, f2a4, 
                    labels = c("A", "", "", ""), 
                    ncol = 4, 
                    nrow = 1, 
                    align = "v"), 
          ggarrange(f2b1, f2b2,
                    f2b3, f2b4, 
                    labels = c("B", rep("", 3)), 
                    ncol = 2, 
                    nrow = 2, 
                    align = "hv", 
                    common.legend = TRUE, 
                    legend = "right", 
                    widths = c(1,1), 
                    vjust = 1), 
          ncol = 1,
          nrow = 2, 
          heights = c(1,2))
